%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer (Part-Time)} % Job title
{Siemens AG} % Organization
{Vienna, Austria} % Location
{Oct. 2018 -- Oct. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a web application using Java/Spring for the Backend and TypeScript/React for the Frontend}
\item {Deployed the application on AWS using EC2 instances and VPC configurations}
\item {Set up GitLab CI/CD for continuous integration and delivery}
\item {Developed an embedded web interface for a sensor prototype using Python/Flask}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Full Stack Software Engineer (Summer Internship)} % Job title
{Iteratec GmbH} % Organization
{Vienna, Austria} % Location
{Jul. 2018 -- Sep. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked on an internal web application, based on Spring and React, used for managing applicant profiles}
\item {Implemented Spring Security filters for authentication/authorization with JWT}
\item {Implemented export functionality of an applicant's profile in PDF using Thymeleaf and Flying Saucer}
\item {Implemented visual reporting with Recharts for showcasing and measuring the KPI of recruiters and events}
\item {Drastically improved the overall code quality through refactoring}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Test Automation Engineer (Freelance)} % Job title
{ANECON Software Design und Beratung GmbH} % Organization
{Vienna, Austria} % Location
{Aug. 2017 -- Dec. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Adapted the in house developed test automation framework A2A to the clients' requirements}
\item {Solely responsible of setting up test automation for DPD (courier) and KSV 1870 (creditor interest protection)}
\item {Closely communicated with clients through on-site development}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Teaching Assistant in IT Security (Part-Time)} % Job title
{Vienna University of Technology} % Organization
{Vienna, Austria} % Location
{Aug. 2014 -- Jan. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented vulnerable systems for students to exploit as part of their homework}
\item {Corrected exams}
\item {Interviewed students on their homework}
\item {Helped in organizing and overseeing an annual CTF contest}
\end{cvitems}
}

%------------------------------------------------

\cventry
{iOS Developer (Part-Time)} % Job title
{APA-IT Informations Technologie GmbH} % Organization
{Vienna, Austria} % Location
{Oct. 2012 -- Aug. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented features for the core iOS product, used to deliver newspaper and magazine issues on the platform}
\item {Ensured consistent quality through implementing unit tests and carrying out manual tests}
\item {Assisted with operations by communicating with clients}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}